### 2018-04-26 contents/tn_sagit_abstract.tex
Updates from ShareLaTeX

\textbf{Methods:} We used SAGIT based group merged tractography to study 36 sex-matched TN subjects (right-sided pain) and 36 controls, examining the following trigeminal related white matter pathways: trigeminal nerve (CN V), pontine decussation (TPT), and thalamocortical fibers (S1). GP classifiers were trained by scrolling a moving window over CN V, TPT, and S1 tractography centroids. Fractional anisotropy (FA), generalized FA (GFA), radial diffusivity (RD), axial diffusivity (AD), and mean diffusivity (MD) metrics were evaluated for both groups, analyzing TN vs. control groups and affected vs. unaffected sides. Classifiers that performed at greater-or-equal-to 70\% accuracy were included.

@@

\textbf{Conclusions:} This is the first study in TN that combines group-wise merged tractography, machine learning classification using GP, and analysis of the complete trigeminal pathways from the the trigeminal peripheral fibers to S1 cortex. This analysis demonstrates that TN is characterized by bilateral changes throughout the trigeminal pathway compared with healthy controls, as well as changes between clinically affected and unaffected sides. The combination of group tractography and machine learning have proven to be a powerful approach for the study of white matter diffusivities.

>>>>

\textbf{Methods:} We used SAGIT based group merged tractography to study 36 sex-matched TN subjects (right-sided pain) and 36 controls, examining the following trigeminal related white matter pathways: trigeminal nerve (CN V), pontine decussation (TPT), and thalamocortical fibres (S1). GP classifiers were trained by scrolling a moving window over CN V, TPT, and S1 tractography centroids. Fractional anisotropy (FA), generalized FA (GFA), radial diffusivity (RD), axial diffusivity (AD), and mean diffusivity (MD) metrics were evaluated for both groups, analyzing TN vs. control groups and affected vs. unaffected sides. Classifiers that performed at greater-or-equal-to 70\% accuracy were included.

@@

\textbf{Conclusions:} This is the first study in TN that combines group-wise merged tractography, machine learning classification using GP, and analysis of the complete trigeminal pathways from the the trigeminal peripheral fibres to S1 cortex. This analysis demonstrates that TN is characterized by bilateral changes throughout the trigeminal pathway compared with healthy controls, as well as changes between clinically affected and unaffected sides. The combination of group tractography and machine learning have proven to be a powerful approach for the study of white matter diffusivities.
